---
title: "Taipan Vignette"
author: "Stephanie Kobakian"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Taipan Vignette}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "centre",
  eval = FALSE)
library(taipan)
```

The Taipan package creates simple shiny surveys. The web applications can be used locally or deployed and allow people to save survey results as tidy data that is ready to use for analysis.

The app was initially created to streamline the process of manually tagging images to create a training set. 
It allows users to provide information regarding entire images, and smaller regions within. It is a survey style tool, with questions being posed for each image and area identified.


## Installation

You can install the development version from Github using:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("srkobakian/taipan")
```

## Usage: coming soon...
